---
title: "purrr example_1"
author: "Kinare, Mayuresh"
date: "5/5/2018"
output:
  html_document:
    theme: united
    highlight: tango
    code_folding: show

---

```{r setup, include=FALSE, echo=TRUE}
#sourcing dependencies
source('/mnt/d/gitRepoCheckout/purrr_testing/dependencies_library.R')
#source('/mnt/d/gitRepoCheckout/purrr_testing/dependencies_download_unzip.R')

```
## Using apply family vs purrr

This is an example from http://data.library.virginia.edu/getting-started-with-the-purrr-package-in-r/


Obtaining a list of names of the files we want to load
```{r, echo=TRUE}

# get all files ending in csv
files <- list.files(pattern = "csv$") 

```


Loading csv files using lapply 
```{r, echo=TRUE}
# read in data normally
dat <- lapply(files, read.csv)
names(dat) <- gsub("\\.csv", "", files) # remove file extension

```

Loading csv files using purrr 
```{r, echo=TRUE}

# read in data using purrr
dat2 <- map(files, read.csv)
names(dat2) <- gsub("\\.csv", "", files)

```

Computation using lapply
```{r, echo=TRUE}
#want to find the mean Open price for each stock. Here is a base R way using lapply and an anonymous function:
  
lapply(dat, function(x)mean(x$Open))

```

Computation using purrr
```{r, echo=TRUE}
#want to find the mean Open price for each stock.
  
map(dat, function(x)mean(x$Open))

```


purrr **map** allows us to bypass the function function. Using a tilda (~) in place of function and a dot (.) in place of x, we can do this:
```{r, echo=TRUE}
#Note that we are not using function as well as not passing x
map(dat, ~mean(.$Open))

```

Multiple types of map allow us to determine the structure of the return
```{r, echo=TRUE}
map_dbl(dat, ~mean(.$Open))

```

We want to extract each stock’s Open price data. In other words, we want to go into each data frame in our list and pull out the Open column. We can do that with lapply as follows:
```{r, echo=TRUE}
lapply(dat, function(x)x$Open)


```

Using purrr **map**
```{r, echo=TRUE}
map(dat, "Open")

```

We often want to plot financial data. 
In this case we want to plot Closing price for each stock and look for trends. 

We will do this with the base R function mapply. 
1. Create a vector of stock names for plot labeling. 2. 2. Set up one row of three plotting regions. 
3. Use mapply to create the plot. 

**NOTE:** The “m” in mapply means “multiple arguments”. In this case we have two arguments: the Closing price and the stock name. Notice that mapply requires the function come first and then the arguments.

```{r}
stocks <- sub("\\.csv","", files)

```


```{r, echo=TRUE, fig.asp=0.4}
par(mfrow=c(1,3))
mapply(function(x,y)plot(x$Close, type = "l", main = y), x = dat, y = stocks)


```

*** 
###### This is a R Markdown document, more information on R Markdown https://rmarkdown.rstudio.com/lesson-1.html